R for Clinical Study Reports and Submission

### 2021-09-17 intro.Rmd
Update intro.Rmd
Co-authored-by: yilong zhang <elong0527@gmail.com>

During the course of this book we will provide a recommended folder structure that is aligned with CRAN submissions of R packages.

>>>>

We recommend using 
[R package folder structure](https://github.com/rstudio/cheatsheets/raw/master/package-development.pdf) 
to organize all the A&R related source code and documentation for a clinical trial A&R project. 
The R package folder structure is well defined and widely used in R community through repositories (e.g. CRAN).

The consistent approach of using R package folder structure 
simplifies the communication for all developers within and across organizations.
